scRNAseq benchmark in want of a title

### 2019-11-04 bmc_article.tex
Updates from Overleaf

We define a pipeline, in R, as a list of functions executed consecutively on the output of the previous one (Figure 0). Each step can include various parameters, all of which must be given alternative values. The \textit{runPipeline} command will then proceed in a step-wise fashion to compute only the parts of the pipelines that have not already been computed. In addition, each step can output evaluation metrics, which together provide a multi-layered evaluation, where variations in a given parameter can be evaluated using all metrics from this point downward in the pipeline. This is especially important because end-point metrics, such as the adjusted Rand index (ARI) for clustering, are not perfect. For example, by far the most important determinant of the ARI is the number of detected clusters: the farther it is from the actual number of subpopulations, the worse the ARI. In this context, one strategy has been to cluster across various resolutions and only consider the results that have the right number of cluster \citep{duoClustering2018}. While this has the virtue of making the results comparable, in practice the number of subpopulations is typically unknown, and tools that operate well in this optimal context might not necessarily be best overall. Clustering results are also very sensitive, and as shown below, might not always capture improvements in earlier steps of the pipeline.

Another motivation for the present framework is that clustering is relatively fragile to variations in the pipeline. We therefore also wanted to capture whether the effect of a given parameter alteration is robust to changes in the rest of the pipeline, or rather specific to a set of other pipeline parameters. We therefore proceeded in a step-wise fashion, first testing a large variety of parameters at the early steps of the pipeline along with only a set of mainstream options downstream, then selecting main alternatives and proceeding to a more detailed benchmark of the next step. The basic pipeline used through most of this paper is described at the bottom of Figure 0.

>>>>

We define a pipeline, in R, as a list of functions executed consecutively on the output of the previous one (Figure 0A). Each step can include various parameters, all of which must be given alternative values. The \textit{runPipeline} command will then proceed in a step-wise fashion to compute only the parts of the pipelines that have not already been computed. In addition, each step can output evaluation metrics, which together provide a multi-layered evaluation, where variations in a given parameter can be evaluated using all metrics from this point downward in the pipeline. This is especially important because end-point metrics, such as the adjusted Rand index (ARI) for clustering, are not perfect. For example, by far the most important determinant of the ARI is the number of detected clusters: the farther it is from the actual number of subpopulations, the worse the ARI. In this context, one strategy has been to cluster across various resolutions and only consider the results that have the right number of cluster \citep{duoClustering2018}. While this has the virtue of making the results comparable, in practice the number of subpopulations is typically unknown, and tools that operate well in this optimal context might not necessarily be best overall. Clustering results are also very sensitive, and as shown below, might not always capture improvements in earlier steps of the pipeline.

Another motivation for the present framework is that clustering is relatively fragile to variations in the pipeline. We therefore also wanted to capture whether the effect of a given parameter alteration is robust to changes in the rest of the pipeline, or rather specific to a set of other pipeline parameters. We therefore proceeded in a step-wise fashion, first testing a large variety of parameters at the early steps of the pipeline along with only a set of mainstream options downstream, then selecting main alternatives and proceeding to a more detailed benchmark of the next step (Figure 0B).
